Phenotypic evolution is more constrained in simpler food webs

### 2019-01-11 manuscript.Rmd
paired down number of keywords
adj affiliation for Chris and add dynamic word count of MS

---
title: Phenotypic evolution is more constrained in simpler food webs
author: 
- Matthew A. Barbour$^{1,2,\ast}$
- Christopher J. Greyson-Gaito$^{1,3}$ 
- Arezoo Sootodeh$^{2}$ 
- Brendan Locke$^{4}$ 
- Jordi Bascompte$^{1}$
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Keywords*: fitness landscape, host-parasitoid, natural selection, G-matrix, community context, ecological networks, evolutionary ecology, eco-evolutionary dynamics.

>>>>

---
title: Phenotypic evolution is more constrained in simpler food webs
author: 
- Matthew A. Barbour$^{1,2,\ast}$
- Christopher J. Greyson-Gaito$^{2,3}$ 
- Arezoo Sootodeh$^{2}$ 
- Brendan Locke$^{4}$ 
- Jordi Bascompte$^{1}$
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid.

*Number of words*: `r wordcountaddin::word_count("manuscript.Rmd")`
